UCD \\MSc Thesis Proposal:\\\emph{Real-time System For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}

### 2014-05-11 paper/proposal.tex
motiviation in progress

New IaaS solutions are available on the market with growing number of supported pricing models. This makes the offering attractive enough to move entire businesses to the Cloud. The availability of different pricing schemes reveals new challenges in already unpredictive Capacity Planning process. Is it better to pay some amount upfront and less hourly rate? Is is better to invest in less heavy utilized instances or maybe in more medium ones? When exactly one pricing scheme becomes more attractive?

\begin{itemize}
  \item For a thesis, a hypothesis (`thesis statement') that you will test in your research.
  \item For a project, identify the work required (e.g. implementation and/or experiment) that needs to be completed. If you are completing a project, make sure to speak with your advisor about the expected deliverables; this will include a written project report.
\end{itemize}

{\bf Motivate your problem.} 
\begin{itemize}
  \item What is the significance of your problem? 
  \item What applications or new opportunities will solving your problem provide?
\end{itemize}

>>>>

New IaaS solutions are available on the market with growing number of supported pricing models. This makes the offering attractive enough to move entire businesses to the Cloud. The availability of different pricing schemes reveals new challenges in already unpredictive Capacity Planning process. Is it better to pay some amount of money upfront and less hourly rate? Is is better to invest in less heavy utilized instances or maybe in more medium ones? When exactly one pricing scheme becomes more attractive?

\begin{itemize}
  \item Thesis statement: An analysis of current utilization of the infrastructure in terms of price effectiveness in dynamic pricing IaaS model. A calculation of optimal configuration and adjustements based on recent data and future trends calculated from the load. 
  \item Project work: The system will accept incoming data from the IaaS provider with utilisation metrics and a number of running instances for a given type (light, medium, heavy, on demand). The data will be stored, analysed in terms of price optimality and graphed on capacity planning dashboard.
\end{itemize}

{\bf Motivation.} 
\begin{itemize}
  \item What is the significance of your problem? 
  \item What applications or new opportunities will solving your problem provide?
\end{itemize}
